Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-15 paper/main.tex
Some light editing of the intro, remove most comments

\todo[inline]{most of phrases containing the word ``isolate'' is gone; doing the
    revision of the result section I realized that we probably should
    ``somehow'' add that clusters should not be all over the place but spatially
    constrained to the parahippocampal and neighbouring cortices, because
    naturalistic stimulus / possibly confounding variables}

@@

\todo[inline]{studies regarding naturalistic stimuli are dropped (Hasson, 2004:
reverse correlation in PPA; Bartels, 2004: GLM, FFA and EBA). That should be okay since we focus on the auditory part which should be clearer now; Hasson /
Bartels might shortly be mentioned in the discussion though}

\todo[inline]{mih: Possibly cite DuPre (2019) and declare that this study is a
    concrete realization; COH: I read it but don't know what/how to cite it for
    any other reason than just to cite it (here or in discussion)}

@@

\todo[inline]{The following review of O'Craven and Wolbers could be shortened.
Keeping the small paragraph regarding Aziz should make the focus on auditory
perception clearer. What do you think?}

\todo[inline]{SE: Der Schwung zu Sprache (wobei speech auch erst am Satzende
kommt) ist zu hart, da kommt man als Leser nicht gut mit}

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality} whereas a study using
spoken sentences yielded mixed results \citep{aziz2008modulation}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing famous faces and familiar places during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
[sighted] participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to haptically explored abstract geometric objects.
% Wolbers: connectivity analysis
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
    cortex, and compares connectivity during visual and haptic paradigm: ``The
    scene-related increase in coupling with the PPA was significantly stronger
    in multiple clusters in occipital cortex under visual than haptic
stimulation (Figure 2B; Table S2)''}

\todo[inline]{following phrasing might be strange but necessary to delineate
from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
but imo that does not say anything about excitation/inhibition; interestingly
Huth mentions PPA during talks but it is not discussed in any paper and despite
being promised none of his group came up with a paper regarding that topic}

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
The reviewed studies usually had three things in common that come along with
advantages but also disadvantages:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed an explicit perceptual judgment task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantages of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

\todo[inline]{SE: make motivation of study clearer; gap in research; how it
    (might) advance(s) the field; make clearer how current study solves the
    problem; COH: I revised this part, it's clearer at least
if I read it now}

@@

\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier
nichts geschrieben; probably something like ``all raw data, scripts, and
results are available under xy as datalad/BIDS dataset''}

>>>>

\todo[inline]{doing the
    revision of the result section I realized that we probably should
    ``somehow'' add that clusters should not be all over the place but spatially
    constrained to the parahippocampal and neighbouring cortices, because
    naturalistic stimulus / possibly confounding variables}

@@

@@

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality} whereas a study using
spoken sentences yielded mixed results \citep{aziz2008modulation}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing famous faces and familiar places during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
[sighted] participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to haptically explored abstract geometric objects.
% Wolbers: connectivity analysis

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.
\todo{phrasing might be strange but aims to delineate
from Huth (2016); they do voxel-wise semantic modeling regarding places in PPA
but imo that does not say anything about excitation/inhibition}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgment task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@
